Turbulence in compact to giant H~II regions

### 2023-04-18 strucfunc_paper.tex
Move appendix D to be a separate PDF file

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newlength\SFwidth
\setlength\SFwidth{0.45\textwidth}
\newcommand\SFtwograph[2]{%
  \includegraphics[width=\SFwidth]{Figures/sf-emcee-#1}
  &  \includegraphics[width=\SFwidth]{Figures/sf-emcee-#2}
}
\newcommand\SFtwocorner[2]{%
  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#1}
  &  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#2}
}

@@

\section{Additional covariance corner plots for model fits}
\label{sec:addit-covar-corn}
Supplementary online-only material.
%\clearpage

\begin{figure*}
  \centering
  \sfcfigggg{OrionS}{OrionLH}{M8}{CarC}
  \caption{
    Corner plots of covariances between
    fitted model parameters
    of \ha{} structure function
    for Galactic \hii{} regions.
  }
  \label{fig:corner-Galactic}
\end{figure*}

\begin{figure*}
  \centering
  \sfcfigg{N346}{Dor}
  \caption{
    Same as figure~\ref{fig:corner-Galactic}
    except for Magellanic Cloud \hii{} regions. 
  }
  \label{fig:corner-MC}
\end{figure*}

\begin{figure*}
  \centering
  \sfcfigggg{HV}{HX}{N595}{N604H}
  \caption{
    Same as figure~\ref{fig:corner-Galactic}
    except for \hii{} regions in more distant
    Local Group Galaxies.
  }
  \label{fig:corner-ExtraGal}
\end{figure*}

\input{table-fit-parameters}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%% END %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newlength\SFwidth
\setlength\SFwidth{0.45\textwidth}
\newcommand\SFtwograph[2]{%
  \includegraphics[width=\SFwidth]{Figures/sf-emcee-#1}
  &  \includegraphics[width=\SFwidth]{Figures/sf-emcee-#2}
}
\newcommand\SFtwocorner[2]{%
  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#1}
  &  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#2}
}

@@

@@

\section{Additional covariance corner plots for model fits}
\label{sec:addit-covar-corn}
Supplementary material
\href{https://github.com/will-henney/javier-strucfunc-paper/blob/main/supplementary_material_strucfunc_paper.pdf}
{available online}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%% END %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}
